Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations

### 2022-02-02 paper2.Rmd
spelling

---
title: "Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations"
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: true
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
always_allow_html: true
---

@@

Given the rampant misinformation around Covid-19, her related vaccinations
[@pathakInfodemicsCOVID19Role2020; @mottaHowRightLeaningMedia2020; 
@shahsavariConspiracyTimeCorona2020] and the slowed rate of vaccinations in the
United States, it is important to uncover what relationship the different
fountains of information and information search vehicles for Covid-19 vaccinations
are associated with compliance with public health recommendations. Table
\@ref(tab:table-model-3) demonstrated just how these different fountains of
information and information search vehicles are associated with real world
consequences through Covid-19 vaccination rates and intentions. The first
takeaway is that receiving or seeking information from a doctor or other medical
profession leads to higher likelihood of completed or planned vaccinations.
While blanket advice like "Healthcare Providers should recommend the vaccine to
their patients" would be ineffective because of the declining number of
Americans with a primary care doctor [@levine_etal20], increasing trust in the
institution of medicine seems to remain a strong predictor of vaccinations. 
<!-- add more here, there is a huge logical and sampling fallacy here --> 
A second major takeaway is that receiving information from a Social Networking
Site like Facebook timeline or Twitter status update was significantly
associated with lower vaccination rates. While we don't know what exact
information was absorbed on these platforms, the lower odds of vaccination
indicate that it was not positive. Much has been attempted between 2020 and 2022
to curb vaccine misinformation on these social networking platforms [see
@bowman20 for an early example]; however, I find evidence that these social
networking platforms nevertheless have a measurable negative impact. Finally,
this study also contributes to the conversation on ethnoracial and
educational differences in vaccine hesitancy. I find in my sample that
Hispanic-Latinos and Asians were more likely than non-Hispanics and non-Asians
to receive or plan to receive a vaccination against Covid-19 (Table
\@ref(tab:table-model-3)). Research in this area has mixed results, with some
studies showcasing consistent findings to these [@bagasra_etal21; @king_etal21],
while others show that Whites have the lowest levels of vaccine hesitancy and
many minorities are much more hesitant [@momplaisir_etal21;
@foxworth21]. My finding that college-educated respondents were more likely seek
vaccination is largely consistent with the broader literature
[@khairat_etal22], though again there are many variations depending on the vaccine
in question and study context [@siddiqui_etal13].

@@

This paper has provided several key findings that can be used to motivate policy
interventions for the Covid-19 vaccination campaigns and in the future for other
information campaigns. However, these findings are not to be taken out of the
context of their limitations. This paper is built off a small survey sample (`r
nrow(rain)`) that was hosted online and anonymously through MTurk, a service
that provides people with micro-jobs. Because of how the website is set up,
respondents are incentivized to fill out surveys as quick as possible and there
were many responses that were poor quality and removed from the sample before
analysis. Moreover, there is no incentive for respondents to be honest in these
surveys. However, each of these limitations are often pointed to as limitations 
of survey research as a whole.

Overall, this research project is important because the vehicles used in
information search impacts the information and quality of information found By
looking at how individuals search, I aim to identify pain points and focus areas
for future interventions in the misinformation process.

>>>>

---
title: "Article 2:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations"
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: true
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
always_allow_html: true
---

@@

Given the rampant misinformation around Covid-19, her related vaccinations
[@pathakInfodemicsCOVID19Role2020; @mottaHowRightLeaningMedia2020; 
@shahsavariConspiracyTimeCorona2020] and the slowed rate of vaccinations in the
United States, it is important to uncover what relationship the different
fountains of information and information search vehicles for Covid-19 vaccinations
are associated with compliance with public health recommendations. Table
\@ref(tab:table-model-3) demonstrated just how these different fountains of
information and information search vehicles are associated with real world
consequences through Covid-19 vaccination rates and intentions. The first
takeaway is that receiving or seeking information from a doctor or other medical
profession was associated with higher likelihood of completed or planned vaccinations.
While blanket advice like "Healthcare Providers should recommend the vaccine to
their patients" would be ineffective because of the declining number of
Americans with a primary care doctor [@levine_etal20], increasing trust in the
institution of medicine seems to remain a strong predictor of vaccinations. 
<!-- add more here, there is a huge logical and sampling fallacy here --> 
A second major takeaway is that receiving information from a Social Networking
Site like Facebook timeline or Twitter status update was significantly
associated with lower vaccination rates. While we don't know what exact
information was absorbed on these platforms, the lower odds of vaccination
indicate that it was not positive. Much has been attempted between 2020 and 2022
to curb vaccine misinformation on these social networking platforms [see
@bowman20 for an early example]; however, I find evidence that these social
networking platforms nevertheless have a measurable negative impact. Finally,
this study also contributes to the conversation on ethnoracial and
educational differences in vaccine hesitancy. I find in my sample that
Hispanic-Latinos and Asians were more likely than non-Hispanics and non-Asians
to receive or plan to receive a vaccination against Covid-19 (Table
\@ref(tab:table-model-3)). Research in this area has mixed results, with some
studies showcasing consistent findings to these [@bagasra_etal21; @king_etal21],
while others show that Whites have the lowest levels of vaccine hesitancy and
many minorities are much more hesitant [@momplaisir_etal21;
@foxworth21]. My finding that college-educated respondents were more likely seek
vaccination is largely consistent with the broader literature
[@khairat_etal22], though again there are many variations depending on the vaccine
in question and study context [@siddiqui_etal13].

@@

This paper has provided several key findings that can be used to motivate policy
interventions for the Covid-19 vaccination campaigns and in the future for other
information campaigns. However, these findings are not to be taken out of the
context of their limitations. This paper is built off a small survey sample (
`r nrow(rain)`) that was hosted online and anonymously through MTurk, a service
that provides people with micro-jobs. Because of how the website is set up,
respondents are incentivized to fill out surveys as quick as possible and there
were many responses that were poor quality and removed from the sample before
analysis. Because of this, there is no incentive for respondents to be honest in
these surveys. However, each of these limitations are often pointed to as
limitations of survey research as a whole. Even given these limitations,
the finding of this paper are interesting contributions to the literature.

Overall, this research project is important because the vehicles used in
information search impacts the information and quality of information found. By
looking at how individuals search, I aim to identified pain points and focus areas
for future interventions (receiving information online; ethnoracial variations; ) in the misinformation process.
